Software architectures for workflow integration in science gateways

### 2016-04-21 paper.tex
Fixed typo and updated abstract

\begin{abstract}
%% Text of abstract
  We investigate software architectures to integrate workflow engines
  in science gateways. Based on our experience with the development
  and operations of the CBRAIN and VIP science gateways, and our past
  involvement in the SHIWA project, we abstract the software
  components and interactions in 6 architectures that we compare using
  metrics measuring integration effort, robustness, extensibility,
  scalability and other specific features. Results show the pros and
  cons of the different architectures. Tight integration and
  sub-tasking require the least amount of integration effort and are
  also the most robust. Most architectures perform the same in terms
  of extensibility. The pool model is the most
  scalable. Meta-workflows are only available in nested workflows and
  workflow import.
\end{abstract}

@@

\begin{table*}
\centering
\rowcolors{1}{white}{gray!25}
\begin{tabular}{ll}
  \textbf{Architecture} & \textbf{System} \\
  \hline
  Tight & \pbox{1.5\columnwidth}{
          Catania Science Gateway Framework~\cite{Ardizzone2012}, 
          Distributed application runtime environment (DARE~\cite{maddineni2012distributed}),
          DECIDE~\cite{ardizzone2012decide}$^{c,n}$, LONI Pipeline Environment$^n$~\cite{dinov2009efficient}
          }
  \\
  Service & \pbox{1.5\columnwidth}{
            Apache Airvata~\cite{marru2011apache}, e-BioInfra~\cite{shahand2015data}$^{w,n}$, HubZero with Pegasus~\cite{CPE:CPE3257}, MoSGrid~\cite{krüger2014mosgrid}$^w$, System in~\cite{wu2010accelerating}, Vine Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual Imaging Platform~\cite{GLAT-13}$^n$, WS-PGRADE/gUSE framework~\cite{Kacsuk2012}, 
            Science gateways in ~\cite{kacsuk2014science}$^w$
            } \\
  Sub-task & CBRAIN and PSOM~\cite{GLAT-16}$^n$, CBRAIN and FSL$^n$\\
  Pool & SHIWA pool~\cite{ROGE-13}\\
  Nested & SHIWA Simulation Platform (Coarse-Grained Interoperability~\cite{terstyanszky2014enabling})$^w$\todo{others}\\
  Import & SHIWA Simulation Platform (Fine-Grained Interoperability)~\cite{plankensteiner-prodan-etal:2013}$^w$
\end{tabular}
\caption{Classification of science gateway based on the architecture used to integrate workflow engines. $^c$: based on the Catania Science Gateway Framework. $^w$: based on WS-PGRADE/gUSE. $^n$: used for neuroimaging.}
\label{table:system-classification}
\end{table*}

>>>>

\begin{abstract}
%% Text of abstract
  We investigate software architectures to integrate workflow engines
  in science gateways. Based on our experience with the development
  and operations of the CBRAIN and VIP science gateways, and our past
  involvement in the SHIWA project, we abstract the software
  components and interactions in 6 architectures. We use these
  architectures to classify 18 existing systems and we compare these
  architectures using metrics measuring integration effort,
  robustness, extensibility, scalability and other specific
  features. Results show the pros and cons of the different
  architectures. Tight integration and sub-tasking require the least
  amount of integration effort and are also the most robust. Most
  architectures perform the same in terms of extensibility. The pool
  model is the most scalable. Meta-workflows are only available in
  nested workflows and workflow import.
\end{abstract}

@@

\begin{table*}
\centering
\rowcolors{1}{white}{gray!25}
\begin{tabular}{ll}
  \textbf{Architecture} & \textbf{Systems} \\
  \hline
  Tight & \pbox{1.5\columnwidth}{
          Catania Science Gateway Framework~\cite{Ardizzone2012}, 
          Distributed application runtime environment (DARE~\cite{maddineni2012distributed}),
          DECIDE~\cite{ardizzone2012decide}$^{c,n}$, LONI Pipeline Environment$^n$~\cite{dinov2009efficient}
          }
  \\
  Service & \pbox{1.5\columnwidth}{
            Apache Airvata~\cite{marru2011apache}, e-BioInfra~\cite{shahand2015data}$^{w,n}$, HubZero with Pegasus~\cite{CPE:CPE3257}, MoSGrid~\cite{krüger2014mosgrid}$^w$, System in~\cite{wu2010accelerating}, Vine Toolkit~\cite{DBLP:journals/scpe/SzejnfeldDKKKKLPTWDNW10}, Virtual Imaging Platform~\cite{GLAT-13}$^n$, WS-PGRADE/gUSE framework~\cite{Kacsuk2012}, 
            Science gateways in ~\cite{kacsuk2014science}$^w$
            } \\
  Sub-task & CBRAIN and PSOM~\cite{GLAT-16}$^n$, CBRAIN and FSL$^n$\\
  Pool & SHIWA pool~\cite{ROGE-13}\\
  Nested & SHIWA Simulation Platform (Coarse-Grained Interoperability~\cite{terstyanszky2014enabling})$^w$\todo{others}\\
  Import & SHIWA Simulation Platform (Fine-Grained Interoperability)~\cite{plankensteiner-prodan-etal:2013}$^w$
\end{tabular}
\caption{Classification of science gateway based on the architecture used to integrate workflow engines. $^c$: based on the Catania Science Gateway Framework. $^w$: based on WS-PGRADE/gUSE. $^n$: used for neuroimaging.}
\label{table:system-classification}
\end{table*}
